---
title: "Journey's Daily Data 2023-24"
format: 
  revealjs:
    theme: default
    embed-resources: false
execute:
  echo: false
---

```{r}
#| label: setup
#| results: hide

## Source the data reading and cleaning script
source("scripts/Data_Cleanup.R")

## Source the graphics preparation script
source("scripts/Graph_Prep.R")
```

# Simple Summaries

## Number of Workout and Training Days

```{r}
tmp <- df |>
  filter(!is.na(workoutday)) |>
  group_by(workoutday,.drop=FALSE) |>
  summarize(freq=n()) |>
  mutate(perc=freq/sum(freq),
         perc_lbl=paste0(formatC(perc*100,format="f",digits=0),"%")) |>
  ungroup()

wod <- ggplot(data=tmp,mapping=aes(x=workoutday,y=perc)) +
  geom_bar(stat="identity",color=clr_bar,fill=fill_bar) +
  geom_text(mapping=aes(label=perc_lbl),vjust=-0.25) +
  scale_y_continuous(name=str_glue("Percentage of {sum(tmp$freq)} Days"),
                     expand=expy_barlbl,labels=scales::label_percent()) +
  scale_x_discrete(name="Workout Day?")

tmp <- df |>
  filter(!is.na(training)) |>
  group_by(training,.drop=FALSE) |>
  summarize(freq=n()) |>
  mutate(perc=freq/sum(freq),
         perc_lbl=paste0(formatC(perc*100,format="f",digits=0),"%")) |>
  ungroup()

trt <- ggplot(data=tmp,mapping=aes(x=training,y=perc)) +
  geom_bar(stat="identity",color=clr_bar,fill=fill_bar) +
  geom_text(mapping=aes(label=perc_lbl),vjust=-0.25) +
  scale_y_continuous(name=str_glue("Percentage of {sum(tmp$freq)} Days"),
                     expand=expy_barlbl,labels=scales::label_percent()) +
  scale_x_discrete(name="Training Type",labels=stringr::str_wrap(tmp$training,15))

wod+trt
```


## Sleep Daily Series

```{r}
ggplot() +
  geom_line(data=df,mapping=aes(x=date,y=sleep),color=clr_bkgline) +
  geom_point(data=df,mapping=aes(x=date,y=sleep,fill=workoutday),
             color=clr_pt,pch=21) +
  geom_vline(data=dfComp,mapping=aes(xintercept=date),
             color=clr_comp,linetype=lty_comp,linewidth=lwd_comp) +
  scale_y_continuous(name="Hours of Sleep") +
  scale_x_date(breaks=brks_date,date_labels=lbls_date) +
  scale_fill_manual(values=fill_wo) +
  theme(axis.title.x=element_blank(),
        legend.position="none") +
  labs(caption="Open points are rest days, red lines are competitions")
```

## Sleep Summary

```{r}
#| fig-width: 5.5
tmp <- df |>
  filter(!is.na(sleep)) |>
  mutate(fsleep=factor(sleep)) |>
  group_by(fsleep) |>
  summarize(freq=n()) |>
  mutate(perc=freq/sum(freq),
         perc_lbl=paste0(formatC(perc*100,format="f",digits=0),"%"))

ggplot(data=tmp,mapping=aes(x=fsleep,y=perc)) +
  geom_bar(stat="identity",color=clr_bar,fill=fill_bar) +
  geom_text(mapping=aes(label=perc_lbl),vjust=-0.25) +
  scale_y_continuous(name=str_glue("Percentage of {sum(tmp$freq)} Days"),
                     expand=expy_barlbl,labels=scales::label_percent()) +
  scale_x_discrete(name="Hours of Sleep")
```


## Body Feels Daily Series

```{r}
ggplot() +
  geom_line(data=df,mapping=aes(x=date,y=body_feel),color=clr_bkgline) +
  geom_point(data=df,mapping=aes(x=date,y=body_feel,fill=workoutday),
             color=clr_pt,pch=21) +
  geom_vline(data=dfComp,mapping=aes(xintercept=date),
             color=clr_comp,linetype=lty_comp,linewidth=lwd_comp) +
  scale_y_continuous(breaks=1:5,limits=c(1,5),
                     labels=stringr::str_wrap(levels(df$fbody_feel),width=10)) +
  scale_x_date(breaks=brks_date,date_labels=lbls_date) +
  scale_fill_manual(values=fill_wo) +
  theme(axis.title=element_blank(),
        legend.position="none") +
  labs(caption="Open points are rest days, red lines are competitions")
```

## Body Feels Summary

```{r}
#| fig-width: 5.5
tmp <- df |>
  filter(!is.na(fbody_feel)) |>
  group_by(fbody_feel,.drop=FALSE) |>
  summarize(freq=n()) |>
  mutate(perc=freq/sum(freq),
         perc_lbl=paste0(formatC(perc*100,format="f",digits=0),"%"))

ggplot(data=tmp,mapping=aes(x=fbody_feel,y=perc)) +
  geom_bar(stat="identity",color=clr_bar,fill=fill_bar) +
  geom_text(mapping=aes(label=perc_lbl),vjust=-0.25) +
  scale_y_continuous(name=str_glue("Percentage of {sum(tmp$freq)} Days"),
                     expand=expy_barlbl,labels=scales::label_percent()) +
  scale_x_discrete(labels=stringr::str_wrap(tmp$fbody_feel,width=10)) +
  theme(axis.title.x=element_blank())
```


## Stress Levels Daily Series

```{r}
ggplot() +
  geom_line(data=df,mapping=aes(x=date,y=stress_lvl),color=clr_bkgline) +
  geom_point(data=df,mapping=aes(x=date,y=stress_lvl,fill=workoutday),
             color=clr_pt,pch=21) +
  geom_vline(data=dfComp,mapping=aes(xintercept=date),
             color=clr_comp,linetype=lty_comp,linewidth=lwd_comp) +
  scale_y_continuous(breaks=1:5,limits=c(1,5),
                     labels=stringr::str_wrap(levels(df$fstress_lvl),width=10)) +
  scale_x_date(breaks=brks_date,date_labels=lbls_date) +
  scale_fill_manual(values=fill_wo) +
  theme(axis.title=element_blank(),
        legend.position="none") +
  labs(caption="Open points are rest days, red lines are competitions")
```

## Stress Levels Summary

```{r}
#| fig-width: 5.5
tmp <- df |>
  filter(!is.na(fstress_lvl)) |>
  group_by(fstress_lvl,.drop=FALSE) |>
  summarize(freq=n()) |>
  mutate(perc=freq/sum(freq),
         perc_lbl=paste0(formatC(perc*100,format="f",digits=0),"%"))

ggplot(data=tmp,mapping=aes(x=fstress_lvl,y=perc)) +
  geom_bar(stat="identity",color=clr_bar,fill=fill_bar) +
  geom_text(mapping=aes(label=perc_lbl),vjust=-0.25) +
  scale_y_continuous(name=str_glue("Percentage of {sum(tmp$freq)} Days"),
                     expand=expy_barlbl,labels=scales::label_percent()) +
  scale_x_discrete(labels=stringr::str_wrap(tmp$fstress_lvl,width=10)) +
  theme(axis.title.x=element_blank())
```

## Stress Sources

```{r}
tmp <- df |> 
  summarize(Relationship=sum(stress_relationship=="Yes"),
            Family=sum(stress_family=="Yes"),
            Friends=sum(stress_friends=="Yes"),
            Lonely=sum(stress_lonely=="Yes"),
            School=sum(stress_school=="Yes"),
            Work=sum(stress_work=="Yes"),
            Track=sum(stress_track=="Yes"),
            Tired=sum(stress_tired=="Yes")) |>
  tidyr::pivot_longer(cols=Relationship:Tired,names_to="Source",values_to="freq") |>
  mutate(perc=freq/sum(freq),
         perc_lbl=paste0(formatC(perc*100,format="f",digits=0),"%"))

ggplot(data=tmp,mapping=aes(x=Source,y=perc)) +
  geom_bar(stat="identity",color=clr_bar,fill=fill_bar) +
  geom_text(mapping=aes(label=perc_lbl),vjust=-0.25) +
  scale_y_continuous(name=str_glue("Percentage of {sum(tmp$freq)} Days with Stress"),
                     expand=expy_barlbl,labels=scales::label_percent()) +
  scale_x_discrete(name="Source of Stress") +
  theme(axis.title.x=element_blank()) +
  labs(caption="Note: some days had multiple stressors.")
```


## Eating Habits Daily Series

```{r}
ggplot() +
  geom_line(data=df,mapping=aes(x=date,y=eat_habits),color=clr_bkgline) +
  geom_point(data=df,mapping=aes(x=date,y=eat_habits,fill=workoutday),
             color=clr_pt,pch=21) +
  geom_vline(data=dfComp,mapping=aes(xintercept=date),
             color=clr_comp,linetype=lty_comp,linewidth=lwd_comp) +
  scale_y_continuous(breaks=1:4,limits=c(1,4),
                     labels=stringr::str_wrap(levels(df$feat_habits),width=10)) +
  scale_x_date(breaks=brks_date,date_labels=lbls_date) +
  scale_fill_manual(values=fill_wo) +
  theme(axis.title=element_blank(),
        legend.position="none") +
  labs(caption="Open points are rest days, red lines are competitions")
```

## Eating Habits Summary

```{r}
#| fig-width: 5.5
tmp <- df |>
  filter(!is.na(feat_habits)) |>
  group_by(feat_habits,.drop=FALSE) |>
  summarize(freq=n()) |>
  mutate(perc=freq/sum(freq),
         perc_lbl=paste0(formatC(perc*100,format="f",digits=0),"%"))

ggplot(data=tmp,mapping=aes(x=feat_habits,y=perc)) +
  geom_bar(stat="identity",color=clr_bar,fill=fill_bar) +
  geom_text(mapping=aes(label=perc_lbl),vjust=-0.25) +
  scale_y_continuous(name=str_glue("Percentage of {sum(tmp$freq)} Days"),
                     expand=expy_barlbl,labels=scales::label_percent()) +
  scale_x_discrete(labels=stringr::str_wrap(tmp$feat_habits,width=10)) +
  theme(axis.title.x=element_blank())
```



## Electrolytes Daily Series

```{r}
ggplot() +
  geom_line(data=df,mapping=aes(x=date,y=as.numeric(felectrolytes)),color=clr_bkgline) +
  geom_point(data=df,mapping=aes(x=date,y=as.numeric(felectrolytes),fill=workoutday),
             color=clr_pt,pch=21) +
  geom_vline(data=dfComp,mapping=aes(xintercept=date),
             color=clr_comp,linetype=lty_comp,linewidth=lwd_comp) +
  scale_y_continuous(breaks=1:4,limits=c(1,4),
                     labels=stringr::str_wrap(levels(df$felectrolytes),width=15)) +
  scale_x_date(breaks=brks_date,date_labels=lbls_date) +
  scale_fill_manual(values=fill_wo) +
  theme(axis.title=element_blank(),
        legend.position="none") +
  labs(caption="Open points are rest days, red lines are competitions")
```

## Electrolytes Summary

```{r}
#| fig-width: 5.5
tmp <- df |>
  filter(!is.na(felectrolytes)) |>
  group_by(felectrolytes,.drop=FALSE) |>
  summarize(freq=n()) |>
  mutate(perc=freq/sum(freq),
         perc_lbl=paste0(formatC(perc*100,format="f",digits=0),"%"))

ggplot(data=tmp,mapping=aes(x=felectrolytes,y=perc)) +
  geom_bar(stat="identity",color=clr_bar,fill=fill_bar) +
  geom_text(mapping=aes(label=perc_lbl),vjust=-0.25) +
  scale_y_continuous(name=str_glue("Percentage of {sum(tmp$freq)} Days"),
                     expand=expy_barlbl,labels=scales::label_percent()) +
  scale_x_discrete(labels=stringr::str_wrap(tmp$felectrolytes,width=15)) +
  theme(axis.title.x=element_blank())
```


## Alcohol Daily Series

```{r}
ggplot() +
  geom_line(data=df,mapping=aes(x=date,y=as.numeric(alcohol)),color=clr_bkgline) +
  geom_point(data=df,mapping=aes(x=date,y=as.numeric(alcohol),fill=workoutday),
             color=clr_pt,pch=21) +
  geom_vline(data=dfComp,mapping=aes(xintercept=date),
             color=clr_comp,linetype=lty_comp,linewidth=lwd_comp) +
  scale_y_continuous(breaks=1:3,limits=c(1,3),
                     labels=stringr::str_wrap(levels(df$alcohol),width=15)) +
  scale_x_date(breaks=brks_date,date_labels=lbls_date) +
  scale_fill_manual(values=fill_wo) +
  theme(axis.title=element_blank(),
        legend.position="none") +
  labs(caption="Open points are rest days, red lines are competitions")
```

## Alcohol Summary

```{r}
#| fig-width: 5.5
tmp <- df |>
  filter(!is.na(alcohol)) |>
  group_by(alcohol,.drop=FALSE) |>
  summarize(freq=n()) |>
  mutate(perc=freq/sum(freq),
         perc_lbl=paste0(formatC(perc*100,format="f",digits=0),"%"))

ggplot(data=tmp,mapping=aes(x=alcohol,y=perc)) +
  geom_bar(stat="identity",color=clr_bar,fill=fill_bar) +
  geom_text(mapping=aes(label=perc_lbl),vjust=-0.25) +
  scale_y_continuous(name=str_glue("Percentage of {sum(tmp$freq)} Days"),
                     expand=expy_barlbl,labels=scales::label_percent()) +
  scale_x_discrete(labels=stringr::str_wrap(tmp$alcohol,width=15)) +
  theme(axis.title.x=element_blank())
```


## Period Daily Series

```{r}
ggplot() +
  geom_line(data=df,mapping=aes(x=date,y=as.numeric(period)),color=clr_bkgline) +
  geom_point(data=df,mapping=aes(x=date,y=as.numeric(period),fill=workoutday),
             color=clr_pt,pch=21) +
  geom_vline(data=dfComp,mapping=aes(xintercept=date),
             color=clr_comp,linetype=lty_comp,linewidth=lwd_comp) +
  scale_y_continuous(breaks=1:2,limits=c(1,2),
                     labels=stringr::str_wrap(levels(df$period),width=15)) +
  scale_x_date(breaks=brks_date,date_labels=lbls_date) +
  scale_fill_manual(values=fill_wo) +
  theme(axis.title=element_blank(),
        legend.position="none") +
  labs(caption="Open points are rest days, red lines are competitions")
```




# Relationships

## Sleep and Stress Level I

:::: {.columns}
::: {.column width="60%"}
```{r}
#| fig-width: 5.5
tmp <- df |>
  filter(!is.na(sleep)) |>
  group_by(sleep,fstress_lvl,.drop=FALSE) |>
  summarize(freq=n()) |>
  mutate(perc=freq/sum(freq),
         perc_lbl=paste0(formatC(perc*100,format="f",digits=0),"%")) |>
  ungroup()

tmp1 <- tmp |>
  group_by(sleep) |>
  summarize(n=sum(freq)) |>
  mutate(lbl=paste0(sleep," h"))

ggplot(data=tmp,mapping=aes(x=factor(sleep),y=fstress_lvl,fill=perc)) +
  geom_tile() +  
  scale_fill_gradient2(low=fill_tile["low"],high=fill_tile["high"]) +  
  geom_text(aes(label=perc_lbl)) +  
  scale_y_discrete(labels=str_wrap(levels(tmp$fstress_lvl),width=12)) +  
  scale_x_discrete(labels=tmp1$lbl,position="top") +  
  theme_journey_tile +  
  labs(caption="% in stress level for each sleep amount")
```
:::

```{r}
tbltmp1 <- xtabs(~sleep,data=df)
tbltmp2 <- xtabs(~fstress_lvl,data=df)
```

::: {.column style="width: 40%; font-size: 60%;"}
- Hours of sleep is number of overnight hours from waking up that morning (i.e., no lag).

- To allow for a chi-square test of association (*next slide*) ...
  - The few days with less than 6 (n=`r cumsum(tbltmp1)[["5"]]`) or more than 9 (n=`r FSA::rcumsum(tbltmp1)[["10"]]`) hours of sleep were combined with 6 and 9 hours to form "&leq;6 h" and "&geq;9 h" categories.
  - The few days with "Tough, but things done" (n=`r tbltmp2[["Tough, but things done"]]`), "Tough, but getting through" (n=`r tbltmp2[["Tough, but getting through"]]`), and "Tears, hanging on" (n=`r tbltmp2[["Tears, hanging on"]]`) levels were combined into one level called "Tough." 
:::
::::

## Sleep and Stress Level II

```{r}
dftmp <- df |>
  select(starts_with("fsleep"),fstress_lvl) |>
  mutate(fstress_lvl=forcats::fct_other(fstress_lvl,
                                        keep=c("Happy, under control",
                                               "Great day, some spots"),
                                        other_level="Tough"),
         fstress_lvl=factor(fstress_lvl,levels=c("Tough",
                                                 "Great day, some spots",
                                                 "Happy, under control")))

tmp <- dftmp |>
  filter(!is.na(fsleep)) |>
  group_by(fsleep,fstress_lvl,.drop=FALSE) |>
  summarize(freq=n()) |>
  mutate(perc=freq/sum(freq),
         perc_lbl=paste0(formatC(perc*100,format="f",digits=0),"%")) |>
  ungroup()

tmp1 <- tmp |>
  group_by(fsleep) |>
  summarize(n=sum(freq)) |>
  mutate(lbl=paste0(fsleep,"\n(n=",n," d)"))

tbltmp <- xtabs(~fstress_lvl+fsleep,data=dftmp)
chitmp <- chisq.test(tbltmp)
```

```{r}
## examining time lag results
chitmp1 <- chisq.test(xtabs(~fstress_lvl+fsleep1,data=dftmp))
chitmp2 <- chisq.test(xtabs(~fstress_lvl+fsleep2,data=dftmp))
chitmp7 <- chisq.test(xtabs(~fstress_lvl+fsleep7,data=dftmp))
```

:::: {.columns}
::: {.column style="width: 40%; font-size: 60%;"}
- While there is some evidence for fewer "tough" days with increasing amount of sleep, ultimately **NO** significant association between hours of sleep and stress level was detected (p=`r formatC(chitmp$p.value,format="f",digits=3)`).
- [*Not shown*] There was no association between stress level and hours of sleep one day (p=`r formatC(chitmp1$p.value,format="f",digits=3)`) and two days (p=`r formatC(chitmp2$p.value,format="f",digits=3)`) previous.
- [*Not shown*] There was a weak association between stress level and hours of sleep seven days previous (p=`r formatC(chitmp7$p.value,format="f",digits=3)`). There were somewhat fewer "tough" stress days than expected with less hours of sleep seven days previous.
:::

::: {.column width="60%"}
```{r}
#| fig-width: 5.5
ggplot(data=tmp,mapping=aes(x=fsleep,y=fstress_lvl,fill=perc)) +
  geom_tile() +  
  scale_fill_gradient2(low=fill_tile["low"],high=fill_tile["high"]) +  
  geom_text(aes(label=perc_lbl)) +  
  scale_y_discrete(labels=str_wrap(tmp$fstress_lvl,width=12)) +  
  scale_x_discrete(labels=tmp1$lbl,position="top") +  
  theme_journey_tile +  
  labs(caption="% in stress level for each sleep amount")
```
:::
::::


## Sleep and Body Feels I

:::: {.columns}
::: {.column width="60%"}
```{r}
#| fig-width: 5.5
tmp <- df |>
  filter(!is.na(sleep)) |>
  group_by(sleep,fbody_feel,.drop=FALSE) |>
  summarize(freq=n()) |>
  mutate(perc=freq/sum(freq),
         perc_lbl=paste0(formatC(perc*100,format="f",digits=0),"%")) |>
  ungroup()

tmp1 <- tmp |>
  group_by(sleep) |>
  summarize(n=sum(freq)) |>
  mutate(lbl=paste0(sleep," h"))

ggplot(data=tmp,mapping=aes(x=factor(sleep),y=fbody_feel,fill=perc)) +
  geom_tile() +  
  scale_fill_gradient2(low=fill_tile["low"],high=fill_tile["high"]) +  
  geom_text(aes(label=perc_lbl)) +  
  scale_y_discrete(labels=str_wrap(levels(tmp$fbody_feel),width=12)) +  
  scale_x_discrete(labels=tmp1$lbl,position="top") +  
  theme_journey_tile +  
  labs(caption="% in body feel level for each sleep amount")
```
:::

```{r}
tbltmp1 <- xtabs(~sleep,data=df)
tbltmp2 <- xtabs(~fbody_feel,data=df)
```

::: {.column style="width: 40%; font-size: 60%;"}
- Hours of sleep is number of overnight hours from waking up that morning (i.e., no lag).

- To allow for a chi-square test of association (*next slide*) ...
  - The few days with less than 6 (n=`r cumsum(tbltmp1)[["5"]]`) or more than 9 (n=`r FSA::rcumsum(tbltmp1)[["10"]]`) hours of sleep were combined with 6 and 9 hours to form "&leq;6 h" and "&geq;9 h" categories.
  - The "Sick/Injured/Can't" level was dropped (n=`r tbltmp2[["Sick/Injured/Can't"]]`).
:::
::::

## Sleep and Body Feels II

```{r}
dftmp <- df |>
  select(starts_with("fsleep"),fbody_feel) |>
  mutate(fbody_feel=forcats::fct_drop(fbody_feel))

tmp <- dftmp |>
  filter(!is.na(fsleep)) |>
  group_by(fsleep,fbody_feel,.drop=FALSE) |>
  summarize(freq=n()) |>
  mutate(perc=freq/sum(freq),
         perc_lbl=paste0(formatC(perc*100,format="f",digits=0),"%")) |>
  ungroup()

tmp1 <- tmp |>
  group_by(fsleep) |>
  summarize(n=sum(freq)) |>
  mutate(lbl=paste0(fsleep,"\n(n=",n," d)"))

tbltmp <- xtabs(~fbody_feel+fsleep,data=dftmp)
chitmp <- chisq.test(tbltmp)
```

```{r}
## examining time lag results
chitmp1 <- chisq.test(xtabs(~fbody_feel+fsleep1,data=dftmp))
chitmp2 <- chisq.test(xtabs(~fbody_feel+fsleep2,data=dftmp))
chitmp7 <- chisq.test(xtabs(~fbody_feel+fsleep7,data=dftmp))
```


:::: {.columns}
::: {.column style="width: 40%; font-size: 55%;"}
- There is **NO** significant association between how your body felt and hours of sleep that day (p=`r formatC(chitmp$p.value,format="f",digits=3)`) and two days previous (p=`r formatC(chitmp2$p.value,format="f",digits=3)`) previous [*Not shown*].
- [*Not shown*] There was an association between how your body felt  and hours of sleep one day previous (p=`r formatC(chitmp1$p.value,format="f",digits=3)`), with slightly fewer than expected "Sore, need trainer" and "Fine, getting it done" days with more sleep (>8 hr) one day previous.
- [*Not shown*] There was an association between how your body felt and hours of sleep seven days previous (p=`r formatC(chitmp7$p.value,format="f",digits=3)`). There were somewhat more than expected "Sore, need trainer" and "Fine, getting it done" days with more sleep and more than expected "Amazing, could PR" days with less sleep seven days previous.
:::

::: {.column width="60%"}
```{r}
#| fig-width: 5.5
ggplot(data=tmp,mapping=aes(x=fsleep,y=fbody_feel,fill=perc)) +
  geom_tile() +  
  scale_fill_gradient2(low=fill_tile["low"],high=fill_tile["high"]) +  
  geom_text(aes(label=perc_lbl)) +  
  scale_y_discrete(labels=str_wrap(tmp$fbody_feel,width=12)) +  
  scale_x_discrete(labels=tmp1$lbl,position="top") +  
  theme_journey_tile +  
  labs(caption="% in body feel level for each sleep amount")
```
:::
::::


## Workouts and Eating Habits I

:::: {.columns}
::: {.column width="60%"}
```{r}
#| fig-width: 5.5
tmp <- df |>
  filter(!is.na(feat_habits)) |>
  group_by(training,feat_habits,.drop=FALSE) |>
  summarize(freq=n()) |>
  mutate(perc=freq/sum(freq),
         perc_lbl=paste0(formatC(perc*100,format="f",digits=0),"%")) |>
  ungroup()

tmp1 <- tmp |>
  group_by(training) |>
  summarize(n=sum(freq)) |>
  mutate(lbl=paste0(str_wrap(training,12),"\n(n=",n," d)"))

ggplot(data=tmp,mapping=aes(x=training,y=feat_habits,fill=perc)) +
  geom_tile() +  
  scale_fill_gradient2(low=fill_tile["low"],high=fill_tile["high"]) +  
  geom_text(aes(label=perc_lbl)) +  
  scale_y_discrete(labels=str_wrap(levels(tmp$feat_habits),width=12)) +  
  scale_x_discrete(labels=tmp1$lbl,position="top") +  
  theme_journey_tile +  
  labs(caption="% in eating habit for each training type")
```
:::

```{r}
tbltmp1 <- xtabs(~training,data=df)
tbltmp2 <- xtabs(~feat_habits,data=df)
```

::: {.column style="width: 40%; font-size: 60%;"}
- To allow for a chi-square test of association (*next slide*) ...
  - The "Competition" days were dropped (n=`r tbltmp1[["Competition"]]`) (*can be added back later when more competitions are added*).
  - The two "Not good, .." levels (n=`r tbltmp2[["Not good, but 3 meals"]]` and `r tbltmp2[["Not good, not 3 meals"]]`) were combined to one "Not good" level. 
:::
::::


## Workouts and Eating Habits II

```{r}
dftmp <- df |>
  select(training,feat_habits) |>
  filter(training!="Competition") |>
  mutate(training=forcats::fct_drop(training),
         feat_habits=forcats::fct_other(feat_habits,
                                        keep=c("3 meals, and balanced",
                                               "3 meals, but upset"),
                                        other_level="Not good"),
         feat_habits=factor(feat_habits,levels=c("Not good",
                                                 "3 meals, but upset",
                                                 "3 meals, and balanced")))

tmp <- dftmp |>
  filter(!is.na(feat_habits)) |>
  group_by(training,feat_habits,.drop=FALSE) |>
  summarize(freq=n()) |>
  mutate(perc=freq/sum(freq),
         perc_lbl=paste0(formatC(perc*100,format="f",digits=0),"%")) |>
  ungroup()

tmp1 <- tmp |>
  group_by(training) |>
  summarize(n=sum(freq)) |>
  mutate(lbl=paste0(training,"\n(n=",n," d)"))

tbltmp <- xtabs(~feat_habits+training,data=dftmp)
chitmp <- chisq.test(tbltmp)
```

:::: {.columns}
::: {.column style="width: 40%; font-size: 60%;"}
- There is a significant association between training type and eating habits (p=`r formatC(chitmp$p.value,format="f",digits=3)`).
- It appears that you eat more balanced meals and fewer "not good" meals on your training days, as compared to your rest days.
:::

::: {.column width="60%"}
```{r}
#| fig-width: 5.5
ggplot(data=tmp,mapping=aes(x=training,y=feat_habits,fill=perc)) +
  geom_tile() +  
  scale_fill_gradient2(low=fill_tile["low"],high=fill_tile["high"]) +  
  geom_text(aes(label=perc_lbl)) +  
  scale_y_discrete(labels=str_wrap(levels(tmp$feat_habits),width=12)) +  
  scale_x_discrete(labels=tmp1$lbl,position="top") +  
  theme_journey_tile +  
  labs(caption="% in eating habit for each training type")
```
:::
::::


## Eating Habits and How Body Feels I

:::: {.columns}
::: {.column width="60%"}
```{r}
#| fig-width: 5.5
dftmp <- df |>
  select(feat_habits,fbody_feel) |>
  filter(!is.na(feat_habits),!is.na(fbody_feel)) |>
  mutate(feat_habits=fct_drop(feat_habits),
         fbody_feel=fct_drop(fbody_feel))

tmp <- dftmp |>
  group_by(feat_habits,fbody_feel,.drop=FALSE) |>
  summarize(freq=n()) |>
  mutate(perc=freq/sum(freq),
         perc_lbl=paste0(formatC(perc*100,format="f",digits=0),"%")) |>
  ungroup()

tmp1 <- tmp |>
  group_by(feat_habits) |>
  summarize(n=sum(freq)) |>
  mutate(lbl=paste0(str_wrap(feat_habits,12),"\n(n=",n," d)"))

ggplot(data=tmp,mapping=aes(x=feat_habits,y=fbody_feel,fill=perc)) +
  geom_tile() +  
  scale_fill_gradient2(low=fill_tile["low"],high=fill_tile["high"]) +  
  geom_text(aes(label=perc_lbl)) +  
  scale_y_discrete(labels=str_wrap(levels(tmp$fbody_feel),width=12)) +  
  scale_x_discrete(labels=tmp1$lbl,position="top") +  
  theme_journey_tile +  
  labs(caption="% in body feels level for each eating habit")
```
:::

```{r}
tbltmp <- xtabs(~feat_habits+fbody_feel,data=dftmp)
chitmp <- chisq.test(tbltmp)
```

::: {.column style="width: 40%; font-size: 60%;"}
- To allow for a chi-square test of association, unused levels of "body feels" and "eating habits" were dropped as on previous slides
- There was **NO** significant association between eating habits for the day and how your body felt that day (p=`r formatC(chitmp$p.value,format="f",digits=3)`).
:::
::::


## Eating Habits and How Body Feels II

:::: {.columns}
::: {.column width="60%"}
```{r}
#| fig-width: 5.5
dftmp <- df |>
  select(feat_habits1,fbody_feel) |>
  filter(!is.na(feat_habits1),!is.na(fbody_feel)) |>
  mutate(feat_habits1=fct_drop(feat_habits1),
         fbody_feel=fct_drop(fbody_feel))

tmp <- dftmp |>
  group_by(feat_habits1,fbody_feel,.drop=FALSE) |>
  summarize(freq=n()) |>
  mutate(perc=freq/sum(freq),
         perc_lbl=paste0(formatC(perc*100,format="f",digits=0),"%")) |>
  ungroup()

tmp1 <- tmp |>
  group_by(feat_habits1) |>
  summarize(n=sum(freq)) |>
  mutate(lbl=paste0(str_wrap(feat_habits1,12),"\n(n=",n," d)"))

ggplot(data=tmp,mapping=aes(x=feat_habits1,y=fbody_feel,fill=perc)) +
  geom_tile() +  
  scale_fill_gradient2(low=fill_tile["low"],high=fill_tile["high"]) +  
  geom_text(aes(label=perc_lbl)) +  
  scale_y_discrete(labels=str_wrap(levels(tmp$fbody_feel),width=12)) +  
  scale_x_discrete(labels=tmp1$lbl,position="top") +  
  theme_journey_tile +  
  labs(caption="% in body feels level for each eating habit")
```
:::

```{r}
tbltmp <- xtabs(~feat_habits1+fbody_feel,data=dftmp)
chitmp1 <- chisq.test(tbltmp)
```

```{r}
dftmp <- df |>
  select(feat_habits2,fbody_feel) |>
  filter(!is.na(feat_habits2),!is.na(fbody_feel)) |>
  mutate(feat_habits2=fct_drop(feat_habits2),
         fbody_feel=fct_drop(fbody_feel))
tbltmp <- xtabs(~feat_habits2+fbody_feel,data=dftmp)
chitmp2 <- chisq.test(tbltmp)

dftmp <- df |>
  select(feat_habits7,fbody_feel) |>
  filter(!is.na(feat_habits7),!is.na(fbody_feel)) |>
  mutate(feat_habits7=fct_drop(feat_habits7),
         fbody_feel=fct_drop(fbody_feel))
tbltmp <- xtabs(~feat_habits7+fbody_feel,data=dftmp)
chitmp7 <- chisq.test(tbltmp)

```

::: {.column style="width: 40%; font-size: 60%;"}
- There was **NO** significant association between eating habits from previous day and how your body felt -- one day previous (p=`r formatC(chitmp1$p.value,format="f",digits=3)`, shown), two days previous (p=`r formatC(chitmp2$p.value,format="f",digits=3)`, *not shown*), and seven days previous (p=`r formatC(chitmp7$p.value,format="f",digits=3)`, *not shown*).
:::
::::



## Eating Habits and Sleep I

:::: {.columns}
::: {.column width="60%"}
```{r}
#| fig-width: 5.5
dftmp <- df |>
  select(feat_habits,fsleep) |>
  filter(!is.na(feat_habits),!is.na(fsleep)) |>
  mutate(feat_habits=fct_drop(feat_habits),
         fsleep=fct_drop(fsleep))

tmp <- dftmp |>
  group_by(feat_habits,fsleep,.drop=FALSE) |>
  summarize(freq=n()) |>
  mutate(perc=freq/sum(freq),
         perc_lbl=paste0(formatC(perc*100,format="f",digits=0),"%")) |>
  ungroup()

tmp1 <- tmp |>
  group_by(feat_habits) |>
  summarize(n=sum(freq)) |>
  mutate(lbl=paste0(str_wrap(feat_habits,12),"\n(n=",n," d)"))

ggplot(data=tmp,mapping=aes(x=feat_habits,y=fsleep,fill=perc)) +
  geom_tile() +  
  scale_fill_gradient2(low=fill_tile["low"],high=fill_tile["high"]) +  
  geom_text(aes(label=perc_lbl)) +  
  scale_y_discrete(labels=str_wrap(levels(tmp$fsleep),width=12)) +  
  scale_x_discrete(labels=tmp1$lbl,position="top") +  
  theme_journey_tile +  
  labs(caption="% in sleep amounts for each eating habit")
```
:::

```{r}
tbltmp <- xtabs(~feat_habits+fsleep,data=dftmp)
chitmp <- chisq.test(tbltmp)
```

::: {.column style="width: 40%; font-size: 60%;"}
- To allow for a chi-square test of association, unused levels of "eating habits" were dropped and sleep amounts were combined as on previous slides
- There **was** a significant association between eating habits for the day and how much you slept that night (p=`r formatC(chitmp$p.value,format="f",digits=3)`). There was a tendency to sleep less when you ate worse (and sleep more when you ate better).
:::
::::


## Eating Habits and Sleep II

:::: {.columns}
::: {.column width="60%"}
```{r}
#| fig-width: 5.5
dftmp <- df |>
  select(feat_habits1,fsleep) |>
  filter(!is.na(feat_habits1),!is.na(fsleep)) |>
  mutate(feat_habits1=fct_drop(feat_habits1),
         fsleep=fct_drop(fsleep))

tmp <- dftmp |>
  group_by(feat_habits1,fsleep,.drop=FALSE) |>
  summarize(freq=n()) |>
  mutate(perc=freq/sum(freq),
         perc_lbl=paste0(formatC(perc*100,format="f",digits=0),"%")) |>
  ungroup()

tmp1 <- tmp |>
  group_by(feat_habits1) |>
  summarize(n=sum(freq)) |>
  mutate(lbl=paste0(str_wrap(feat_habits1,12),"\n(n=",n," d)"))

ggplot(data=tmp,mapping=aes(x=feat_habits1,y=fsleep,fill=perc)) +
  geom_tile() +  
  scale_fill_gradient2(low=fill_tile["low"],high=fill_tile["high"]) +  
  geom_text(aes(label=perc_lbl)) +  
  scale_y_discrete(labels=str_wrap(levels(tmp$fsleep),width=12)) +  
  scale_x_discrete(labels=tmp1$lbl,position="top") +  
  theme_journey_tile +  
  labs(caption="% in sleep amounts for each eating habit")
```
:::

```{r}
tbltmp <- xtabs(~feat_habits1+fsleep,data=dftmp)
chitmp1 <- chisq.test(tbltmp)
```

```{r}
dftmp <- df |>
  select(feat_habits2,fsleep) |>
  filter(!is.na(feat_habits2),!is.na(fsleep)) |>
  mutate(feat_habits2=fct_drop(feat_habits2),
         fsleep=fct_drop(fsleep))
tbltmp <- xtabs(~feat_habits2+fsleep,data=dftmp)
chitmp2 <- chisq.test(tbltmp)

dftmp <- df |>
  select(feat_habits7,fsleep) |>
  filter(!is.na(feat_habits7),!is.na(fsleep)) |>
  mutate(feat_habits7=fct_drop(feat_habits7),
         fsleep=fct_drop(fsleep))
tbltmp <- xtabs(~feat_habits7+fsleep,data=dftmp)
chitmp7 <- chisq.test(tbltmp)
```

::: {.column style="width: 40%; font-size: 60%;"}
- There was **NO** significant association between eating habits from previous days and how much you slept that day -- one day previous (p=`r formatC(chitmp1$p.value,format="f",digits=3)`, shown), two days previous (p=`r formatC(chitmp2$p.value,format="f",digits=3)`, *not shown*), and seven days previous (p=`r formatC(chitmp7$p.value,format="f",digits=3)`, *not shown*).
- There was slight evidence (but not significant) that you slept more on the day following when you did not eat well (*shown*).
:::
::::



## Electrolytes and How Body Feels I

:::: {.columns}
::: {.column width="60%"}
```{r}
#| fig-width: 5.5
dftmp <- df |>
  select(electrolytesb,fbody_feel) |>
  filter(!is.na(electrolytesb),!is.na(fbody_feel)) |>
  mutate(electrolytesb=fct_drop(electrolytesb),
         fbody_feel=fct_drop(fbody_feel))

tmp <- dftmp |>
  group_by(electrolytesb,fbody_feel,.drop=FALSE) |>
  summarize(freq=n()) |>
  mutate(perc=freq/sum(freq),
         perc_lbl=paste0(formatC(perc*100,format="f",digits=0),"%")) |>
  ungroup()

tmp1 <- tmp |>
  group_by(electrolytesb) |>
  summarize(n=sum(freq)) |>
  mutate(lbl=paste0(str_wrap(electrolytesb,12),"\n(n=",n," d)"))

ggplot(data=tmp,mapping=aes(x=electrolytesb,y=fbody_feel,fill=perc)) +
  geom_tile() +  
  scale_fill_gradient2(low=fill_tile["low"],high=fill_tile["high"]) +  
  geom_text(aes(label=perc_lbl)) +  
  scale_y_discrete(labels=str_wrap(levels(tmp$fbody_feel),width=12)) +  
  scale_x_discrete(labels=tmp1$lbl,position="top") +  
  theme_journey_tile +  
  labs(caption="% in body feels level for each electrolytes level")
```
:::

```{r}
tbltmp <- xtabs(~electrolytesb+fbody_feel,data=dftmp)
chitmp <- chisq.test(tbltmp)
```

::: {.column style="width: 40%; font-size: 60%;"}
- To allow for a chi-square test of association, unused levels of "body feels" were dropped and electrolyte levels were pooled into "yes" (had electrolytes) or "no"
- There was **NO** significant association between having electrolytes for the day and how your body felt that day (p=`r formatC(chitmp$p.value,format="f",digits=3)`).
:::
::::


## Electrolytes and How Body Feels II

:::: {.columns}
::: {.column width="60%"}
```{r}
#| fig-width: 5.5
dftmp <- df |>
  select(electrolytesb1,fbody_feel) |>
  filter(!is.na(electrolytesb1),!is.na(fbody_feel)) |>
  mutate(electrolytesb1=fct_drop(electrolytesb1),
         fbody_feel=fct_drop(fbody_feel))

tmp <- dftmp |>
  group_by(electrolytesb1,fbody_feel,.drop=FALSE) |>
  summarize(freq=n()) |>
  mutate(perc=freq/sum(freq),
         perc_lbl=paste0(formatC(perc*100,format="f",digits=0),"%")) |>
  ungroup()

tmp1 <- tmp |>
  group_by(electrolytesb1) |>
  summarize(n=sum(freq)) |>
  mutate(lbl=paste0(str_wrap(electrolytesb1,12),"\n(n=",n," d)"))

ggplot(data=tmp,mapping=aes(x=electrolytesb1,y=fbody_feel,fill=perc)) +
  geom_tile() +  
  scale_fill_gradient2(low=fill_tile["low"],high=fill_tile["high"]) +  
  geom_text(aes(label=perc_lbl)) +  
  scale_y_discrete(labels=str_wrap(levels(tmp$fbody_feel),width=12)) +  
  scale_x_discrete(labels=tmp1$lbl,position="top") +  
  theme_journey_tile +  
  labs(caption="% in body feels level for each electrolyte level")
```
:::

```{r}
tbltmp <- xtabs(~electrolytesb1+fbody_feel,data=dftmp)
chitmp1 <- chisq.test(tbltmp)
```

```{r}
dftmp <- df |>
  select(electrolytesb2,fbody_feel) |>
  filter(!is.na(electrolytesb2),!is.na(fbody_feel)) |>
  mutate(electrolytesb2=fct_drop(electrolytesb2),
         fbody_feel=fct_drop(fbody_feel))
tbltmp <- xtabs(~electrolytesb2+fbody_feel,data=dftmp)
chitmp2 <- chisq.test(tbltmp)

dftmp <- df |>
  select(electrolytesb7,fbody_feel) |>
  filter(!is.na(electrolytesb7),!is.na(fbody_feel)) |>
  mutate(electrolytesb7=fct_drop(electrolytesb7),
         fbody_feel=fct_drop(fbody_feel))
tbltmp <- xtabs(~electrolytesb7+fbody_feel,data=dftmp)
chitmp7 <- chisq.test(tbltmp)

```

::: {.column style="width: 40%; font-size: 60%;"}
- There was **NO** significant association between having electrolytes on previous days and how your body felt -- one day previous (p=`r formatC(chitmp1$p.value,format="f",digits=3)`, shown), two days previous (p=`r formatC(chitmp2$p.value,format="f",digits=3)`, *not shown*), and seven days previous (p=`r formatC(chitmp7$p.value,format="f",digits=3)`, *not shown*).
:::
::::



## Alcohol and How Body Feels I

:::: {.columns}
::: {.column width="60%"}
```{r}
#| fig-width: 5.5
dftmp <- df |>
  select(alcoholb,fbody_feel) |>
  filter(!is.na(alcoholb),!is.na(fbody_feel)) |>
  mutate(alcoholb=fct_drop(alcoholb),
         fbody_feel=fct_drop(fbody_feel))

tmp <- dftmp |>
  group_by(alcoholb,fbody_feel,.drop=FALSE) |>
  summarize(freq=n()) |>
  mutate(perc=freq/sum(freq),
         perc_lbl=paste0(formatC(perc*100,format="f",digits=0),"%")) |>
  ungroup()

tmp1 <- tmp |>
  group_by(alcoholb) |>
  summarize(n=sum(freq)) |>
  mutate(lbl=paste0(str_wrap(alcoholb,12),"\n(n=",n," d)"))

ggplot(data=tmp,mapping=aes(x=alcoholb,y=fbody_feel,fill=perc)) +
  geom_tile() +  
  scale_fill_gradient2(low=fill_tile["low"],high=fill_tile["high"]) +  
  geom_text(aes(label=perc_lbl)) +  
  scale_y_discrete(labels=str_wrap(levels(tmp$fbody_feel),width=12)) +  
  scale_x_discrete(labels=tmp1$lbl,position="top") +  
  theme_journey_tile +  
  labs(caption="% in body feels level for each alcohol level")
```
:::

```{r}
tbltmp <- xtabs(~alcoholb+fbody_feel,data=dftmp)
chitmp <- chisq.test(tbltmp)
```

::: {.column style="width: 40%; font-size: 60%;"}
- To allow for a chi-square test of association, unused levels of "body feels" were dropped and alcohol levels were pooled into "yes" (had electrolytes) or "no"
- There was **NO** significant association between consuming alcohol for the day and how your body felt that day (p=`r formatC(chitmp$p.value,format="f",digits=3)`).
:::
::::


## Alcohol and How Body Feels II

:::: {.columns}
::: {.column width="60%"}
```{r}
#| fig-width: 5.5
dftmp <- df |>
  select(alcoholb1,fbody_feel) |>
  filter(!is.na(alcoholb1),!is.na(fbody_feel)) |>
  mutate(alcoholb1=fct_drop(alcoholb1),
         fbody_feel=fct_drop(fbody_feel))

tmp <- dftmp |>
  group_by(alcoholb1,fbody_feel,.drop=FALSE) |>
  summarize(freq=n()) |>
  mutate(perc=freq/sum(freq),
         perc_lbl=paste0(formatC(perc*100,format="f",digits=0),"%")) |>
  ungroup()

tmp1 <- tmp |>
  group_by(alcoholb1) |>
  summarize(n=sum(freq)) |>
  mutate(lbl=paste0(str_wrap(alcoholb1,12),"\n(n=",n," d)"))

ggplot(data=tmp,mapping=aes(x=alcoholb1,y=fbody_feel,fill=perc)) +
  geom_tile() +  
  scale_fill_gradient2(low=fill_tile["low"],high=fill_tile["high"]) +  
  geom_text(aes(label=perc_lbl)) +  
  scale_y_discrete(labels=str_wrap(levels(tmp$fbody_feel),width=12)) +  
  scale_x_discrete(labels=tmp1$lbl,position="top") +  
  theme_journey_tile +  
  labs(caption="% in body feels level for each alcohol level")
```
:::

```{r}
tbltmp <- xtabs(~alcoholb1+fbody_feel,data=dftmp)
chitmp1 <- chisq.test(tbltmp)
```

```{r}
dftmp <- df |>
  select(alcoholb2,fbody_feel) |>
  filter(!is.na(alcoholb2),!is.na(fbody_feel)) |>
  mutate(alcoholb2=fct_drop(alcoholb2),
         fbody_feel=fct_drop(fbody_feel))
tbltmp <- xtabs(~alcoholb2+fbody_feel,data=dftmp)
chitmp2 <- chisq.test(tbltmp)

dftmp <- df |>
  select(alcoholb7,fbody_feel) |>
  filter(!is.na(alcoholb7),!is.na(fbody_feel)) |>
  mutate(alcoholb7=fct_drop(alcoholb7),
         fbody_feel=fct_drop(fbody_feel))
tbltmp <- xtabs(~alcoholb7+fbody_feel,data=dftmp)
chitmp7 <- chisq.test(tbltmp)

```

::: {.column style="width: 40%; font-size: 60%;"}
- There was **NO** significant association between consuming alcohol on previous days and how your body felt -- one day previous (p=`r formatC(chitmp1$p.value,format="f",digits=3)`, shown), two days previous (p=`r formatC(chitmp2$p.value,format="f",digits=3)`, *not shown*), and seven days previous (p=`r formatC(chitmp7$p.value,format="f",digits=3)`, *not shown*).
:::
::::




## Alcohol and Stress I

:::: {.columns}
::: {.column width="60%"}
```{r}
#| fig-width: 5.5
dftmp <- df |>
  select(alcoholb,fstress_lvl) |>
  filter(!is.na(alcoholb),!is.na(fstress_lvl)) |>
  mutate(alcoholb=fct_drop(alcoholb),
         fstress_lvl=forcats::fct_other(fstress_lvl,
                                        keep=c("Happy, under control",
                                               "Great day, some spots"),
                                        other_level="Tough"),
         fstress_lvl=factor(fstress_lvl,levels=c("Tough",
                                                 "Great day, some spots",
                                                 "Happy, under control")),
         fstress_lvl=fct_drop(fstress_lvl))

tmp <- dftmp |>
  group_by(alcoholb,fstress_lvl,.drop=FALSE) |>
  summarize(freq=n()) |>
  mutate(perc=freq/sum(freq),
         perc_lbl=paste0(formatC(perc*100,format="f",digits=0),"%")) |>
  ungroup()

tmp1 <- tmp |>
  group_by(alcoholb) |>
  summarize(n=sum(freq)) |>
  mutate(lbl=paste0(str_wrap(alcoholb,12),"\n(n=",n," d)"))

ggplot(data=tmp,mapping=aes(x=alcoholb,y=fstress_lvl,fill=perc)) +
  geom_tile() +  
  scale_fill_gradient2(low=fill_tile["low"],high=fill_tile["high"]) +  
  geom_text(aes(label=perc_lbl)) +  
  scale_y_discrete(labels=str_wrap(levels(tmp$fstress_lvl),width=12)) +  
  scale_x_discrete(labels=tmp1$lbl,position="top") +  
  theme_journey_tile +  
  labs(caption="% in body feels level for each alcohol level")
```
:::

```{r}
tbltmp <- xtabs(~alcoholb+fstress_lvl,data=dftmp)
chitmp <- chisq.test(tbltmp)
```

::: {.column style="width: 40%; font-size: 60%;"}
- To allow for a chi-square test of association, a singular "tough" stress level was created (as preciously) and alcohol levels were pooled into "yes" (had electrolytes) or "no"
- There was **NO** significant association between consuming alcohol for the day and stress levels that day (p=`r formatC(chitmp$p.value,format="f",digits=3)`).
:::
::::


## Alcohol and Stress II

:::: {.columns}
::: {.column width="60%"}
```{r}
#| fig-width: 5.5
dftmp <- df |>
  select(alcoholb1,fstress_lvl) |>
  filter(!is.na(alcoholb1),!is.na(fstress_lvl)) |>
  mutate(alcoholb1=fct_drop(alcoholb1),
         fstress_lvl=forcats::fct_other(fstress_lvl,
                                        keep=c("Happy, under control",
                                               "Great day, some spots"),
                                        other_level="Tough"),
         fstress_lvl=factor(fstress_lvl,levels=c("Tough",
                                                 "Great day, some spots",
                                                 "Happy, under control")),
         fstress_lvl=fct_drop(fstress_lvl))

tmp <- dftmp |>
  group_by(alcoholb1,fstress_lvl,.drop=FALSE) |>
  summarize(freq=n()) |>
  mutate(perc=freq/sum(freq),
         perc_lbl=paste0(formatC(perc*100,format="f",digits=0),"%")) |>
  ungroup()

tmp1 <- tmp |>
  group_by(alcoholb1) |>
  summarize(n=sum(freq)) |>
  mutate(lbl=paste0(str_wrap(alcoholb1,12),"\n(n=",n," d)"))

ggplot(data=tmp,mapping=aes(x=alcoholb1,y=fstress_lvl,fill=perc)) +
  geom_tile() +  
  scale_fill_gradient2(low=fill_tile["low"],high=fill_tile["high"]) +  
  geom_text(aes(label=perc_lbl)) +  
  scale_y_discrete(labels=str_wrap(levels(tmp$fstress_lvl),width=12)) +  
  scale_x_discrete(labels=tmp1$lbl,position="top") +  
  theme_journey_tile +  
  labs(caption="% in body feels level for each alcohol level")
```
:::

```{r}
tbltmp <- xtabs(~alcoholb1+fstress_lvl,data=dftmp)
chitmp1 <- chisq.test(tbltmp)
```

```{r}
dftmp <- df |>
  select(alcoholb2,fstress_lvl) |>
  filter(!is.na(alcoholb2),!is.na(fstress_lvl)) |>
  mutate(alcoholb2=fct_drop(alcoholb2),
         fstress_lvl=forcats::fct_other(fstress_lvl,
                                        keep=c("Happy, under control",
                                               "Great day, some spots"),
                                        other_level="Tough"),
         fstress_lvl=factor(fstress_lvl,levels=c("Tough",
                                                 "Great day, some spots",
                                                 "Happy, under control")),
         fstress_lvl=fct_drop(fstress_lvl))
tbltmp <- xtabs(~alcoholb2+fstress_lvl,data=dftmp)
chitmp2 <- chisq.test(tbltmp)

dftmp <- df |>
  select(alcoholb7,fstress_lvl) |>
  filter(!is.na(alcoholb7),!is.na(fstress_lvl)) |>
  mutate(alcoholb7=fct_drop(alcoholb7),
         fstress_lvl=forcats::fct_other(fstress_lvl,
                                        keep=c("Happy, under control",
                                               "Great day, some spots"),
                                        other_level="Tough"),
         fstress_lvl=factor(fstress_lvl,levels=c("Tough",
                                                 "Great day, some spots",
                                                 "Happy, under control")),
         fstress_lvl=fct_drop(fstress_lvl))
tbltmp <- xtabs(~alcoholb7+fstress_lvl,data=dftmp)
chitmp7 <- chisq.test(tbltmp)

```

::: {.column style="width: 40%; font-size: 60%;"}
- There was **NO** significant association between consuming alcohol on previous days and stress level -- one day previous (p=`r formatC(chitmp1$p.value,format="f",digits=3)`, shown), two days previous (p=`r formatC(chitmp2$p.value,format="f",digits=3)`, *not shown*), and seven days previous (p=`r formatC(chitmp7$p.value,format="f",digits=3)`, *not shown*).
- However, there is weak evidence for more "Happy, under control" days when having consumed alcohol the previous day (*shown*)
:::
::::




## Period and Sleep

:::: {.columns}
::: {.column width="60%"}
```{r}
#| fig-width: 5.5
dftmp <- df |>
  select(period,fsleep) |>
  filter(!is.na(period),!is.na(fsleep)) |>
  mutate(period=fct_drop(period),
         fsleep=fct_drop(fsleep))

tmp <- dftmp |>
  group_by(period,fsleep,.drop=FALSE) |>
  summarize(freq=n()) |>
  mutate(perc=freq/sum(freq),
         perc_lbl=paste0(formatC(perc*100,format="f",digits=0),"%")) |>
  ungroup()

tmp1 <- tmp |>
  group_by(period) |>
  summarize(n=sum(freq)) |>
  mutate(lbl=paste0(str_wrap(period,12),"\n(n=",n," d)"))

ggplot(data=tmp,mapping=aes(x=period,y=fsleep,fill=perc)) +
  geom_tile() +  
  scale_fill_gradient2(low=fill_tile["low"],high=fill_tile["high"]) +  
  geom_text(aes(label=perc_lbl)) +  
  scale_y_discrete(labels=str_wrap(levels(tmp$fsleep),width=12)) +  
  scale_x_discrete(labels=tmp1$lbl,position="top") +  
  theme_journey_tile +  
  labs(caption="% in sleep amounts for each eating habit")
```
:::

```{r}
tbltmp <- xtabs(~period+fsleep,data=dftmp)
chitmp <- chisq.test(tbltmp)
```

::: {.column style="width: 40%; font-size: 60%;"}
- To allow for a chi-square test of association sleep amounts were combined as on previous slides
- There was **NO** a significant association between being on your period and how much you slept that night (p=`r formatC(chitmp$p.value,format="f",digits=3)`).
:::
::::


## Period and Stress

:::: {.columns}
::: {.column width="60%"}
```{r}
#| fig-width: 5.5
dftmp <- df |>
  select(period,fstress_lvl) |>
  filter(!is.na(period),!is.na(fstress_lvl)) |>
  mutate(period=fct_drop(period),
         fstress_lvl=forcats::fct_other(fstress_lvl,
                                        keep=c("Happy, under control",
                                               "Great day, some spots"),
                                        other_level="Tough"),
         fstress_lvl=factor(fstress_lvl,levels=c("Tough",
                                                 "Great day, some spots",
                                                 "Happy, under control")),
         fstress_lvl=fct_drop(fstress_lvl))

tmp <- dftmp |>
  group_by(period,fstress_lvl,.drop=FALSE) |>
  summarize(freq=n()) |>
  mutate(perc=freq/sum(freq),
         perc_lbl=paste0(formatC(perc*100,format="f",digits=0),"%")) |>
  ungroup()

tmp1 <- tmp |>
  group_by(period) |>
  summarize(n=sum(freq)) |>
  mutate(lbl=paste0(str_wrap(period,12),"\n(n=",n," d)"))

ggplot(data=tmp,mapping=aes(x=period,y=fstress_lvl,fill=perc)) +
  geom_tile() +  
  scale_fill_gradient2(low=fill_tile["low"],high=fill_tile["high"]) +  
  geom_text(aes(label=perc_lbl)) +  
  scale_y_discrete(labels=str_wrap(levels(tmp$fstress_lvl),width=12)) +  
  scale_x_discrete(labels=tmp1$lbl,position="top") +  
  theme_journey_tile +  
  labs(caption="% in body feels level for each period level")
```
:::

```{r}
tbltmp <- xtabs(~period+fstress_lvl,data=dftmp)
chitmp <- chisq.test(tbltmp)
```

::: {.column style="width: 40%; font-size: 60%;"}
- To allow for a chi-square test of association, a singular "tough" stress level was created (as preciously)
- There was **NO** significant association between being on your period and stress level that day (p=`r formatC(chitmp$p.value,format="f",digits=3)`).
:::
::::
